Phenology and Mycorrhizae Manuscript

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd
Added relative humidity download

#Download Photosynthetically active radiation (PAR)
```{r}
dataName="NEON_PAR"
NEON_ID='DP1.00024.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
inFileName <- "PARPAR_30min.csv"
# varName <- "precipBulk"

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)

@@

selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
inFileName <- "ST_30_minute.csv"

@@

>>>>

#Download Photosynthetically active radiation (PAR)
```{r}
dataName="NEON_PAR"
NEON_ID='DP1.00024.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
inFileName <- "PARPAR_30min.csv"
varName <- "PARMean"

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
funType=mean
funName="mean"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

funType=min
funName="min"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

funType=max
funName="max"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

#Download Relative Humidity
```{r}
dataName="NEON_RH"
NEON_ID='DP1.00098.001'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
# selectColumns <- c('verticalPosition','PARMean','PARMinimum','PARMaximum','PARVariance','PARFinalQF')
# inFileName <- "PARPAR_30min.csv"
# varName <- "PARMean"

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
# combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
#                 inFileName=inFileName,dataPath=dataPath)
# funType=mean
# funName="mean"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=min
# funName="min"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=max
# funName="max"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

@@

selectColumns <- c('horizontalPosition','verticalPosition','soilTempMean','soilTempMinimum','soilTempMaximum','finalQF')
inFileName <- "ST_30_minute.csv"
varName <- 'soilTempMean'

@@

funType=mean
funName="mean"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

funType=min
funName="min"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

funType=max
funName="max"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
